On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-06 MS.tex
Add Ian suggestion (2/2)

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}. The net result is that the growth advantage experienced by high SLA species at small sizes, dissapates among larger plants. While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

>>>>

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass. Overall, the models fit did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the models (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}. The net result is that the growth advantage experienced by high SLA species at small sizes, dissipates by the time large plante size are attained. While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended. Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}. In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
